\documentclass[11pt]{l3deliverable}
\usepackage[table]{xcolor}
\usepackage{geometry}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}
\newcolumntype{T}{>{\centering\arraybackslash}m{0.20\textwidth}}
\newcolumntype{L}{>{\centering\arraybackslash}m{0.74\textwidth}}
\definecolor{medium-red}{rgb}{0.35,0,0}
\hypersetup{colorlinks, linkcolor={medium-red}, citecolor={medium-red},
urlcolor={medium-red}}
\geometry{a4paper}
\setlength\parindent{0pt}
\title{Acceptance Test Report}
\deliverableID{D8.3}
\project{PSD3 Group Exercise 2}
\team{W}
\version{1.0}
\author{
    Gordon Reid: 1002536R\\
    Ryan Wells: 1002253W\\
    Kristopher Stewart: 1007175S\\
    David Selkirk: 1003646S\\
    James Gallagher: 0800899G\\
}
\date{\today}

\begin{document}

\maketitle

\newpage

\tableofcontents

\newpage

\section{Introduction}

\subsection{Identification}

This is the acceptance test report completed by Team W based on the acceptance
test plan created by Team W and ran on an complete system implementation
of the internship management system supplied by Team V. The internship
management system is for Software Engineering (SE) and Electronic and
Software Engineering (ESE) students, studying in the School of Computing
Science.

\subsection{Related Documentation}

PSD3 Group Exercise Description:

\url{http://fims.moodle.gla.ac.uk/file.php/128/coursework/psd3-ge-2.pdf}

PSD3 Requirements Specification:

\url{fims.moodle.gla.ac.uk/file.php/128/coursework/requirements-specification-ge2.pdf}

\subsection{Purpose and Description Of Document}

This document serves as the Acceptance Test Report based on the test cases
created by Team W, ran on the internship management implementation by Team V.

\newpage

\section{Testing}

\subsection{Approve Accepted Offer}

\input{aao.tex}

\subsection{Login}

\input{l.tex}

\newpage

\subsection{Notify Accepted Offer}

\input{nao.tex}

\newpage

\subsection{Publish Advertisement}

\input{pa.tex}

\newpage

\subsection{Register Employer}

\input{re.tex}

\newpage

\subsection{Submit Advertisement}

\input{sa.tex}

\newpage

\subsection{View Advertisement}

\input{vas.tex}

\newpage

\subsection{View Student Detail}

\input{vsd.tex}

\newpage

\section{Summary}

\subsection{Supplied Data}

The implementation supplied was incomplete with assignAcademicVisitor(),
recordVisitAssessment(), and createNewSelfSourcedRole(). These methods however
are not necessarily required for the must have use cases.

The implementation has no compiled JavaDoc and, after inspection, the
implementation lacks JavaDoc entirely.

There was a large block comment specifying usernames contained within the
system however only the course coordinator information was supplied. Secondly,
the team's tests used a different user name for student (100000 instead of
stu) however neither successfully login.

There was also no build directory and thus no INSTALL.txt.

In addition, there was no README.txt to know how to contact the team. The
team looked out to the third year computing science Facebook group to contact
the team. This was successful however the team themselves were not entirely
sure how the implementation worked.

These issues meant that modifying our test set up was impossible to conduct
while maintaining the black box testing benefits.

\subsection{Overall test results}

The entire test suite comprised of forty test cases. Of those there were two
failures and twenty seven errors (all java.lang.NullPointerException).

The test cases which passed are exhaustively listed below:

\begin{enumerate}
	\item Student login with incorrect password.
	\item Student login with incorrect username.
	\item Employer login with incorrect password.
	\item Employer login with incorrect username.
	\item Course Coordinator login with correct credentials.
	\item Course Coordinator with incorrect password.
	\item Course Coordinator with incorrect username.
	\item Course Coordinator notifying they have accepted an internship.
	\item Course Coordinator submits an advertisement.
	\item Course Coordinator tries to view details of a nonexistent student.
	\item Course Coordinator registers a new employer.
\end{enumerate}

\subsection{Failed Use Cases}

\subsubsection{Approve Accepted Offer}

The approve accepted offer fails because login fails. Login fails because the
supplied data for student and employers appears to be incorrect and there is
no way to set up a user.

\subsubsection{Login}

The login use case failed for students and employers. As we were only able to
use the supplied data, the failing cannot be entirely verified. One can only
assume that the supplied data for students and employers is incorrect.

\subsubsection{Notify Accepted Offer}

The notify accepted offer fails because login fails. Login fails because the
supplied data for student and employers appears to be incorrect and there is
no way to set up a user.

\subsubsection{Publish Advertisement}

The publish advertisement use case fails because login fails. Login fails 
because the supplied data for student and employers appears to be incorrect and 
there is no way to set up a user.

In addition to this there is an assumption that the advertisement to be
published exists. If publishing a non-existent advertisement is attempted the
application crashes from a null pointer exception.

\subsubsection{Register Employer}

The publish advertisement use case fails because login fails. Login fails 
because the supplied data for student and employers appears to be incorrect and 
there is no way to set up a user.

\subsubsection{Submit Advertisement}

The submit advertisement use case fails because login fails. Login fails 
because the supplied data for student and employers appears to be incorrect and 
there is no way to set up a user.

\subsubsection{View Advertisement}

The submit advertisement use case fails because login fails. Login fails 
because the supplied data for student and employers appears to be incorrect and 
there is no way to set up a user.

In addition advert publication failing also causes the use case to fail.

\subsubsection{View Student Detail}

\end{document}
